COG-ED Manuscript

### 2021-12-08 06_Paper/COG-ED/Manuscript.Rmd
update mlm model h2b
expansion of the mlm model
adding simple slopes analysis

  h2b_data <- cbind(data_SV, dprime["d"], rt["meanrt"])

@@

  # d'
  h2b_data$d.mwc <- ave(h2b_data$d, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_data$d.cwc <- h2b_data$d - h2b_data$d.mwc

  # mRT
  h2b_data$meanrt.mwc <- ave(h2b_data$meanrt, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_data$meanrt.cwc <- h2b_data$meanrt - h2b_data$meanrt.mwc

  # level
  h2b_data$level.mwc <- ave(h2b_data$level, h2b_data$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_data$level.cwc <- h2b_data$level - h2b_data$level.mwc

  ## no level 2 predictors

  # null model -----------------------------------------------------------------
  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
                 data = h2b_data)

@@

  m1_h2b <- lmer(sv ~ level.cwc + d.cwc + meanrt.cwc + (level.cwc|subject), 
                 data = h2b_data,
                 REML = T) # parameters estimated by maximizing restricted log-likelihood

  # (1) if a warning message is produced, check random effects
    summary(m1_h2b)$varcor
    # (11) if all SDs are different from 0 and correlations look good (unequal to zero)
      # this message should be a false positive and this model can be reported
    # (12) if (11) is not true, check all available optimizers
      n_cores <- parallel::detectCores()
      opt_cl <- makeCluster(n_cores, type = "SOCK")
      clusterEvalQ(opt_cl, library("lme4"))
      clusterExport(opt_cl, "h2b_data")
      m1_h2b_all <- allFit(m1_h2b, parallel = "snow", ncpus = n_cores, cl = opt_cl) 
      stopCluster(opt_cl)
      summary(m1_h2b_all)$msgs
      # (121) if an optimizer returns NULL, use this optimizer and recalculate model to get the final model

  # (2) if (121) is not true OR a singular fit message occurs, check for potential outliers and recalculate
    potential_outliers_m1_h2b <- subset(h2b_data, abs(scale(resid(m1_h2b))) > 3)    
    percentage_outliers <- 100/nrow(h2b_data) * nrow(potential_outliers_m1_h2b)
    # get new subset excluding outliers
    h2b_data_norm <- droplevels(subset(h2b_data, abs(scale(resid(m1_h2b))) < 3))
    # start with (1) again

  # (3) if (1) and (2) do not help, start reducing the model stepwise

  ## plot model fit of the final model ----
  plot_model(mfinal_h2b, type = "diag")

  # FIXME: do we want to include  a table like Table 3. in Westbrook et al.?
    # if we decide to include a table of mlm results, I propose to include a table with
    # term/parameter - Beta - SE - p-value - random effects (SD)

@@

>>>>

  agg_vars <- cbind(data_SV, dprime["d"])
  h2b_data <- merge(agg_vars, data_nback, by = c("subject", "level"))

  data_nfc$subject[which(data_nfc$subject == "E12K08")] <- "E12K08_neu"

  h2b_data <- merge(h2b_data, data_nfc, by = "subject")

  # include new variable for post-correct trials
  h2b_data$postcorrect = rep(NA, length(h2b_data$correct))    # add empty column
      for (z in 1:(length(h2b_data$correct)-1)) {             # for all trials except the very last one
        if (h2b_data$correct[z] == 1) {                       # if correct, paste correct
          h2b_data$postcorrect[z+1] <- 1
        } else if (h2b_data$correct[z] == 0) {                # if not correct, paste incorrect
          h2b_data$postcorrect[z+1] <- 0
        } else {
          h2b_data$postcorrect[z+1] <- NA                     # if empty, leave empty
        } 
      }

  # 512 trials, 8 blocks á 64 trials
  i <- 1
  while (i <= nrow(h2b_data)){
    for (j in 1:64) {
      h2b_data$trial <- seq(1, 64, 1)
    }
    i <- i + 64
  }

  h2b_data$postcorrect[h2b_data$trial == "1"] <- 1         # avoid transfer from previous block and subject (first trial of a block is always correct)

  # get subset for MLM

  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)
                               & rt > 0.1))

@@

  # d'
  h2b_sub$d.mwc <- ave(h2b_sub$d, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$d.cwc <- h2b_sub$d - h2b_sub$d.mwc

  # RT
  h2b_sub$rt.mwc <- ave(h2b_sub$rt, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$rt.cwc <- h2b_sub$rt - h2b_sub$rt.mwc

  # level
  h2b_sub$level.mwc <- ave(h2b_sub$level, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$level.cwc <- h2b_sub$level - h2b_sub$level.mwc

  # correct 
  h2b_sub$correct.mwc <- ave(h2b_sub$correct, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$correct.cwc <- h2b_sub$correct - h2b_sub$correct.mwc

  # postcorrect
  h2b_sub$postcorrect.mwc <- ave(h2b_sub$postcorrect, h2b_sub$subject, FUN = function(x) mean(x, na.rm = T))
  h2b_sub$postcorrect.cwc <- h2b_sub$postcorrect - h2b_sub$postcorrect.mwc

  ## level 2 predictor
  # > CGM

  # NFC
  h2b_sub$nfc.cgm <- scale(h2b_sub$nfc, scale = F)

  # null model -----------------------------------------------------------------
  m0_h2b <- lmer(sv ~ 1 + (1|subject), 
                 data = h2b_sub)

@@

  m1_h2b <- lmer(sv ~ level.cwc * nfc.cgm + d.cwc + rt.cwc + correct.cwc + postcorrect.cwc + (level.cwc|subject), 
                 data = h2b_sub,
                 REML = T) # parameters estimated by maximizing restricted log-likelihood

  ## plot model fit of the final model ----
  library(sjPlot)
  plot_model(m1_h2b, type = "diag")

  # simple slopes analysis -----------------------------------------------------
  library(interactions)

  m1_h2b.ss <- sim_slopes(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none", 
                    cond.int = T,                                       # print conditional intercepts
                    johnson_neyman = T, jnplot = T, control.fdr = T)    # calculate Johnson Neyman intervals, 
                                                                        # create plot, adjust false discovery rate
  library(huxtable)
  as_huxtable(m1_h2b.ss)

  plot(m1_h2b.ss)

  interact_plot(m1_h2b, pred = level.cwc, modx = nfc.cgm, centered = "none",
                x.label = "n back load level", y.label = "subjective value", legend.main = "NFC", interval = T) + theme_apa()

  names(summary(m1_h2b))
  m1_h2b.fixef <- summary(m1_h2b)$coefficients
  m1_h2b.ranef <- as.data.frame(summary(m1_h2b)$varcor)
  write.csv2(te.norm.fixef, file = "S4_te.norm.fixef.csv")
  write.csv2(te.norm.ranef, file = "S4_te.norm.ranef.csv")

@@

intraclass correlation "icc_h2b"
table withterm/parameter - Beta - SE - p-value - random effects (SD)
huxtable?
